Drivers of sex differences in consumption

### 2017-05-29 sex-difference/sex-difference.Rmd
sex difference

```{r load_data}
year = 2011
bene = read_tsv(sprintf('../bene_%i.tsv', year)) %>%
  filter(between(age, 66, 96), hmo_months==0, sex %in% c('male', 'female')) %>%
  mutate(is_female=sex=='female', is_white=race=='white')

pde = read_tsv(sprintf('../pde_%i.tsv', year)) %>%
  filter(bene_id %in% bene$bene_id)

@@

```{r drug_by_sex_plot}
ubs %>%
  select(antibiotic, sex, cpkp) %>%
  spread(sex, cpkp) %>%
  ggplot(aes(x=male, y=female, label=antibiotic)) +
  geom_label() +
  geom_point() +
  geom_abline() +
  xlab('claims per 1,000 male beneficiaries') +
  ylab('claims per 1,000 female beneficiaries') +
  theme_minimal()
```

>>>>

```{r load_data}
year = 2011
bene = read_tsv(sprintf('../bene_%i.tsv', year)) %>%
  mutate(is_female=sex=='female', is_white=race=='white')

pde = read_tsv(sprintf('../pde_%i.tsv', year))

@@

```{r drug_by_sex_plot}
ubs %>%
  ggplot(aes(x=male, y=female, label=antibiotic)) +
  geom_text() +
  geom_point() +
  geom_abline() +
  xlab('claims per 1,000 male beneficiaries') +
  ylab('claims per 1,000 female beneficiaries') +
  theme_minimal() +
  coord_fixed()
```
